---
title: "Introduction to tswbench"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tswbench)
library(data.table)
```

## Basic usage

tswbench provides quick access to Tushare Pro (https://tushare.pro/) data. In order
to query data from Tushare, simply create an tsapi object and access Tushare api
functions using "$".

```{r}
# set token first
# SetToken("YOUR TUSHARE TOKEN")
api <- TushareApi()

# argument formats are same as official documents
eod <- api$daily(trade_date = "20200701")
eod[]
```

## API function usage

You can get help from API usage functions. To query all supported functions:

```{r}
tsapi_func()
```

Find specific funcion usage:

```{r}
tsapi_usage("daily", what = "arg")
```

```{r}
tsapi_usage("daily", what = "field")
```

## End-of-day data

tswbench wraps various end-of-day data functions to market_eod() to simplify 
data acquisition. market_eod() supports most of Tushare APIs.

### Query end-of-day intraday OHLC:

Intraday data is not officially documented. However, data can be queried by special
"intraday" func.

```{r}
ohlc <- market_eod(func = "intraday", date = "20200701", freq = 60)
ohlc[]
```

### Query end-of-day index performance:

```{r}
index <- market_eod(func = "index_daily", date = "20200701")
index[]
```

## Fundamental data

tswbench also wraps various fundamental reports to report_market() to query
whole market per year and quarter, and report_quarter() to query quaterly reports
per ts_code. These functions handle update_flag and always return latest updated 
data.

```{r}
income2020q1 <- report_market(type = "income", y = 2020, q = 1)
income2020q1[]
```

## Standardise A-share symbols

Different vendors may use different coding schemes for A-share traded securities.
These symbols can be standardised to code and traded exchange by parse_ashare_code().
Or convert to Tushare standard by norm_ashare_code(). 

```{r}
ts_code <- norm_ashare_code(code = c("000001.sz", "sh600000", "601989"), type = "stock")
ts_code
```


## Realtime data

Realtime data provided by Tushare Pro is not officially documented. Experimental
support is provided by tushare_realtime_websocket(). Data handling is provided by
user defined callback function, which should accept at least three arguments:
  - topic : a character vector of length 1
  - code: a character vector of length 1
  - record: a character vector of various lengths depending on the topic

Here is an example simple prints received data to console:

```{r eval=FALSE}

# define a callback function to handle realtime data
# the call back function should accept at least three arguments:
#   

simple_callback <- function(topic, code, record, ...) {
  cat("topic:  ", topic, "\n")
  cat("code:   ", code, "\n")
  cat("record: ")
  str(record)

  TRUE
}

# connect to Tushare service
ws <- tushare_realtime_websocket(topic = "some_topic", code = "000001.SZ", callback = simple_callback)
ws$connect()

```

## Third party realtime data vendors

Realtime data provided by other vendors are provided, namely by Sina and Tencent.
Data can be easily fetched calling sina_realtime_quote(), tencent_realtime_quote() and
tencent_realtime_moneyflow().

An example of querying all stocks traded from Sina:

```{r}

# fetch all traded stocks from Tushare:
api <- TushareApi()
stocks <- api$stock_basic()
# convert ts_code to Sina format
codes <- sina_ashare_code(stocks$ts_code)
# query from Sina
quotes <- sina_realtime_quote(codes)
quotes[]
```

### Keeping track of Sina realtime data

A simple incremental model is created to record and track Sina realtime data. Due
to the single-thread nature of R, we need to query Sina data in a separate R process:

```{r eval=FALSE}
# define an sqlite database file
db <- "/path/to/data.db"
# run data query loop
sina_realtime_loop(db)
```

On our working R process, a incremental data loader can be created and used to 
fetch newly arrived data:

```{r eval=FALSE}
db <- "/path/to/data.db"
ld <- sina_realtime_loader(db)

# get new data
quotes <- ld()
# consume data
quotes[, spread := Bid - Ask]
summary(quotes$spread)
# do other thins with quotes

# get updated data
quotes <- ld()
```

Please notice that PRAGMA WAL is used on the sqlite database, so data R process and 
working R process must be on same machine.

## Fast online algorithms

tswbench provides a set of stateful online functions for realtime data processing.
All online functions are created by calling corresponding make_*() functions. Please
refer to manual to find full list of supported algorithms.

```{r}

# calculate triple exponential moving average
tema <- make_tema(period = 12)
data <- runif(10, max = 10)
value <- tema(data)
# the generated function tema() is stateful, thus suitable for incremental calculation
new_data <- runif(2, max = 10)
new_value <- tema(new_data)

```

```{r}

# supported algorithm are usually pretty fast

  n = 10000
  w = 120

  # moving quantile
  x <- runif(n)
  probs <- seq(0, 1, 0.25)
  f <- make_moving_quantile(window = w, probs = probs)

  t1 <- system.time({y1 <- f(x)})
  t2 <- system.time({y2 <- zoo::rollapply(x, 120, quantile, probs = probs, type = 3, fill = NA, align = "right")})
  
  #speed-up
  t2 / t1
```

